Effect of Physical Treatment in Electrical Conductivity of SU-8-based Carbon Structures

### 2020-03-14 myPapers/SU8_PhysicalTreatment/Effect_of_Physical_Treatment_in_Electrical_Conductivity_of_SU8based_Carbon_Structures/article.tex
img update

\bgroup
\fixFloatSize{images/8b20b7c4-6432-49d6-aeab-5f61950533fe-umethod.png}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{images/8b20b7c4-6432-49d6-aeab-5f61950533fe-umethod.png}{\includegraphics{images/8b20b7c4-6432-49d6-aeab-5f61950533fe-umethod.png}}{}
\makeatother 
\caption{{Schematic diagram of the SU-8 carbon film fabrication process. a) . b) . c) . d) . e) . f) . g) . h) . i) . j) . k) . l) . }}
\label{f-471d296f0590}
\end{figure*}
\egroup

@@

\section{Nomenclature}
[TODO: Add used acronyms and their meaning]
\begin{table}[!htbp]
\def\arraystretch{1}
\ignorespaces 
\centering 
\begin{tabulary}{\linewidth}{LL}
\tbltoprule 
 &
  \\
\tblbottomrule 
\end{tabulary}\par 
\end{table}

>>>>

\bgroup
\fixFloatSize{images/345cc1b7-01c7-4e66-8e93-81ad0f990362-umethod.png}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{images/345cc1b7-01c7-4e66-8e93-81ad0f990362-umethod.png}{\includegraphics{images/345cc1b7-01c7-4e66-8e93-81ad0f990362-umethod.png}}{}
\makeatother 
\caption{{Schematic diagram of the SU-8 carbon film fabrication process. }}
\label{f-471d296f0590}
\end{figure*}
\egroup

@@

\section{Nomenclature}
[TODO: Add used acronyms and their meaning]
\begin{table}[!htbp]
\def\arraystretch{1}
\ignorespaces 
\centering 
\begin{tabulary}{\linewidth}{LL}
\tbltoprule 
\textbf{PDMS} \mbox{}\protect\newline \textbf{UV} &
  Polydimethylsiloxane \mbox{}\protect\newline Ultraviolet\\
\tblbottomrule 
\end{tabulary}\par 
\end{table}
